Collective excitations in competing phases in two and three dimensions

### 2024-01-24 paper/main.tex
uni

>>>>

\begin{figure}
    \centering
    \includegraphics[width=.48\textwidth]{plots/phase_limits.pdf}
    \caption{The lower left corner ($U<0$ and $V<0$) of the phase diagram obtained for the extended Hubbard model on 
    (a) a square lattice and (b) a simple cubic lattice using a mean-field approximation at temperature $T=0$.
    The blue shading indicates the region where the $s$-wave superconducting phase is the proper ground state of the system.
    The green shading shows the region that we cannot access because it the discretization $N_\gamma$, which is required to accurately describe the system, is too large.
    Lastly, the orange shading shows the region in which the dynamical matrix $\mM$ has negative eigenvalues, indicating that there are phases not captured by our methods.}
    \label{fig:phase_limits}
\end{figure}
